A Case Study in Preserving a High Energy Physics Application

### 2014-03-03 paper.tex
content modification: section 5

\begin{table*}
    \centering
    \begin{tabular}{|l|r|r|r|}
        \hline
        Solution ID & Data Resources & Software Resources & Operation Manual \\ \hline
        Solution 1& grid & CMSSW Git HTTP & email \\ \hline
        Solution 2 and 3& local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
        Solution 4& package & package & shell script + packaging utility \\ \hline
    \end{tabular}
    \caption{The relationship of different solutions}
    \label{table:relationship}
\end{table*}

@@

\subsection{Relationship of Different Solutions}
The relationship of these three solutions to repeat one program is shown in Table~\ref{table:relationship}. The aim is to make it easier to repeat one program through making the data and software preparation easier.

@@

\subsection{Evaluation of Solution 2}
The breakdown of execution time of Solution 2 is shown in Table~\ref{table:time-2nd}. About half of the total execution time is consumed to prepare relevant software environment. The cvs command is forked to check out 23 packages from CMSSW and three git repositories are cloned.

@@

The size of data and software from each category is shown in table~\ref{table:datasize-2nd}.

@@

\subsection{Evaluation of Solution 4}
The breakdown of execution time of the Solution 4 is illustrated in Table~\ref{table:time-3rd}. The time used to obtain file namelist and generate P1 is greatly longer than the execution time within the new package. however, the time consumption of file namelist acquisition and package generation is one-time. That is, once the package is generated, many users can directly obtain the package and repeat the experiment separately.

@@

The data size of Solution 4 is shown in Table~\ref{table:datasize-3rd}. The
data categories is more complex than our imagination. Except the data stored in
Hadoop and the necessary set of software, files from {\tt /pscratch, /sbin, /lib} and other
paths are also necessary for the reproduction of the program.

@@

The packaging utility checks the system call of each file within the namelist,
and maintains the minimum dataset, which makes the size of the final package 
as small as possible. The total size of Hadoop under Solution 2 is astonishing,
while the size of Hadoop under the package is decreased to 20GB. The same trend
applies to the size of CMSSW\_5\_3\_11\_patch3. Because the packaging utility
tries to construct one independent and self-contained package, necessary files
from {\tt /sbin, /lib} and other directories are also copied into the package and
denoted as "Other data for Package" in Table~\ref{table:datasize-2nd3rd}.

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
     Data Category & Data Size & Data Size \\
    & Solution 2 & Solution 4\\ \hline
    HDFS & 43.3GB & 20GB \\ \hline
    PanFS & 155TB & 1.6MB \\ \hline
    CVMFS & 7.4GB &103MB \\ \hline
    NFS & 862GB &53KB \\ \hline
    AFS & 10.2GB &34MB \\ \hline
    Local FS& 110GB&68.3MB \\ \hline
    Total & 156TB &21GB \\ \hline
    \end{tabular}
    \caption{Data Size Comparison beweeen Solution 2 and 4}
    \label{table:datasize-2nd3rd}
\end{table}

@@

Table~\ref{table:time-2nd3rd} shows the execution time comparison between
Solution 2 and 3. The time consumption of the reproduction of one program from
different scholars kept the same under Solution 2, including software and data
preparation. However, under Solution 4, the data and software preparation is
one-time. The following reproduction of the same program only needs to obtain
one copy of the package and execute the actual experimental analysis directly.
Data is obtained through accessing Hadoop Distributed File System in Solution 2, but is copied into the package in Solution 4. This localization of data speeds up the data analysis process, resulting the actual analysis time reducing from 31 minutes to 13 minutes.

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    Task Category & Execution Time & Execution Time \\
    & Solution 2 & Solution 4\\ \hline
    Software Acquisition & 8min 11s & N/A \\ \hline
    Environment Building & 5min 49s  & 3s \\ \hline
    Obtain file namelist & N/A & 28min 23s \\ \hline
    Generate the package & N/A & 85min 51s \\ \hline
    Actual Analysis & 20min 31s & 13min 4s \\ \hline
    \end{tabular}
    \caption{Execution Time Comparison between Solution 2 and 4}
    \label{table:time-2nd3rd}
\end{table}

>>>>

\begin{table*}
    \centering
    \begin{tabular}{|l|r|r|r|}
        \hline
        Solution ID & Data Resources & Software Resources & Operation Manual \\ \hline
        Solution 1& grid & CMSSW Git HTTP & email \\ \hline
        Solution 2 and 3& local (HDFS) & CMSSW Git HTTP & shell script \\ \hline
        Solution 4& package & package & user manual of package \\ \hline
    \end{tabular}
    \caption{The relationship of different solutions}
    \label{table:relationship}
\end{table*}

@@

\subsection{Relationship of Different Solutions}
The relationship of these four solutions to repeat one program is shown in Table~\ref{table:relationship}. Each new solution tries to make it easier to repeat one program through making the data and software preparation easier.

@@

\subsection{Evaluation of Solution 2}
The breakdown of execution time of Solution 2 is shown in Table~\ref{table:time-2nd}. About 40\%  of the total execution time is consumed to prepare relevant software environment. The cvs command is called to check out 23 packages from CMSSW and three git repositories are cloned.

@@

This solution does not support mining of implicit dependencies.
The size of data and software from each category is shown in table~\ref{table:datasize-2nd}, which only lists the size of each clear dependency.

@@

\subsection{Evaluation of Solution 4}

The breakdown of execution time of the
Solution 4 is illustrated in Table~\ref{table:time-3rd}. The time used to
obtain filename list and generate P1 is greatly longer than the execution time
within the new package. However, the time consumption of filename list
acquisition and package generation is one-time. That is, once the package is
generated, many users can directly obtain the package and repeat the experiment
separately.

@@

The data size of Solution 4 is shown in Table~\ref{table:datasize-3rd}. The
data categories are more complex than our imagination. Except the data stored in
Hadoop and the necessary set of software, files from local filesystem and several remote filesystems, such as PanFS, CVMFS, NFS, and AFS, are also necessary for the reproduction of the program.

@@

The packaging utility checks the system call of each file within the namelist,
and maintains the minimum dataset, which makes the size of the final package 
as small as possible. The total size of Hadoop under Solution 2 is astonishing,
while the size of Hadoop under the package is decreased to 20GB. 
The total size of PanFS is 155TB, however, the size of the really used data of PanFS is only 1.6MB.
Table~\ref{table:datasize-2nd3rd} compares the original size and the really used size of each data source.
Solution 4 reduces the total size of all data sources from 156TB to 21GB.

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
     Data Category & Solution2: Size & Solution4: Size \\ \hline
    HDFS & 43.3GB & 20GB \\ \hline
    PanFS & 155TB & 1.6MB \\ \hline
    CVMFS & 7.4GB &103MB \\ \hline
    NFS & 862GB &53KB \\ \hline
    AFS & 10.2GB &34MB \\ \hline
    Local FS& 110GB&68.3MB \\ \hline
    Total & 156TB &21GB \\ \hline
    \end{tabular}
    \caption{Data Size Comparison beweeen Solution 2 and 4}
    \label{table:datasize-2nd3rd}
\end{table}

@@

Table~\ref{table:time-2nd3rd} shows the execution time comparison between
Solution 2 and 4. The time consumption of the reproduction of one program from
different scholars kept the same under Solution 2, including software and data
preparation. However, under Solution 4, the data and software preparation is
one-time. The following reproduction of the same program only needs to obtain
one copy of the package and execute the actual experimental analysis directly.
Data is obtained through accessing HDFS in Solution 2, but is copied into the package in Solution 4. This localization of experimental data speeds up the data analysis process, resulting the actual analysis time reducing from 20 minutes to 13 minutes.

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    Task Category & Solution 2: Time & Solution 4: Time\\ \hline
    Software Acquisition & 8min 11s & N/A \\ \hline
    Environment Build & 5min 49s  & 3s \\ \hline
    Obtain file namelist & N/A & 28min 23s \\ \hline
    Generate package & N/A & 85min 51s \\ \hline
    Actual Analysis & 20min 31s & 13min 4s \\ \hline
    \end{tabular}
    \caption{Execution Time Comparison between Solution 2 and 4}
    \label{table:time-2nd3rd}
\end{table}
